### 2021-04-02 Chapter-3/Chapter-3.tex
update

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis. In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results. For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen. Moreover, translating the machine code into IRs can casue a significant overhead for the trace analysis, as we will discuss in the dissertation.

@@

An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers.

>>>>

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis. In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results. For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen. Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.

@@

An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable.
